---
title       : My First Slides
subtitle    : Examples
author      : JDP
job         : QA
logo        : logo.png
biglogo     : logo.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]    # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Welcome

<hr/>
<h2>Hello</h2>
I am JDP.

---

## My Details

I am a **NZ** citizen.

--- &radio

## Question 1

What is 1 + 1?

1. 1
2. _2_
3. 3
4. 4

*** .hint
This is a hint

*** .explanation
This is an explanation

--- &radio

## Question 2

What are values that x can take to satisfy the following quadratic equation?
<p>
$x^2$ - x - 6 = 0
</p>

1. 2, 3
2. 2, -3
3. _-2, 3_
4. -2, -3
5. None of the above

*** .hint

Factorise or use formula $$\frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$$ to find OR substitute and check

*** .explanation

Sum of roots = -1<br/>
Product of roots = -6<br/>
Hence factors are (x + 2) and (x - 3)

---

## Check Chunk Execution ##
  
```{r scplot, dev = 'png', fig.width = 8, fig.height = 5, error = T}
library(ggplot2); 
qplot(wt, mpg, data = mtcars) 
```

*** =pnotes

```{r ref.label = "scplot", echo = T, eval = F}
```

--- #myslide

<script>
$('#myslide').on('slideenter', function(){
  $(this).find('article')
    .append('<iframe src="http://bl.ocks.org/mbostock/raw/1256572/"></iframe>')
});
$('#myslide').on('slideleave', function(){
  $(this).find('iframe').remove();
});
</script>
